### 2016-03-09 paper/algorithm.tex

Swarm Fusion has two main parameters $\alpha_i$ and $\beta_i$ (for each
thread $T_i$), determining the processing flow of the algorithm: In each
fusion step, the thread collects $\alpha_i$ solution proposals from the
proposal pool and $\beta_i$ solutions from the solution pool, following
a user-defined strategy or at random to be simple.
%
% One can further customize how to pick certain proposal generation
% schemes (as in ~\cite{delong}) or solutions.
Swarm Fusion framework is very flexible and yields various data
processing architectures as shown in Figure~\ref{fig:model}.
%
\begin{figure}[tb]
 \includegraphics[width=\columnwidth]{figure/model.pdf} \caption{Swarm
 Fusion architecture and its relationships to existing methods. mention
 that hierarchical fusion works in a different way, but we can still
 consider that to be our special case, by letting each thread not using
 its own solution in the next fusion.}\label{fig:model}
\end{figure}
%
The bottom right configuration is the most general one, in which we
always fuse some solution proposals and some concurrent solutions
(i.e., $\alpha\ne 0, \beta \ne 0$).
%
Each fusion is multi-way (not binary) with a non-submodular energy, and
we use TRW~\cite{kolmogorov} for the fusion, while any other compatible
inference techniques can be used~\cite{opengm}. Of course, if one knows
that a certain fusion step is a binary fusion with submodular energy,
one can use graph-cuts instead~\cite{alpha_expansion_paper}. If a
certain fusion step is a binary fusion with non-submodular energy, one
can use QPBO~\cite{second_order_smoothness_stereo}.
%
Note that the threads are all synchronized in the figure for a
illustration purpose. In practice, all the threads run asynchronously
with a (read-write) lock on the data in the two pools (See Algorithm~\ref{algorithm:sf}).
%The asynchronous processing could be difficult for cloud parallel
%computing.
%
%
%
\begin{algorithm}
 \caption{Swarm Fusion method}
 \label{algorithm:sf}
 \begin{algorithmic}
  %\Procedure{Swarm Fusion method} {}
  \Procedure{} {$\alpha, \beta$}
  \State $\mathcal{S}_{pool} \leftarrow \emptyset$ //
  Solution pool
  \State Initialize $\mathcal{P}_{pool}$ // Proposal pool
  \ForEach{thread $T_i$}
  \State Initialize its solution $S_i$
  \EndFor
  \State
  \ForEach{thread $T_i$ in parallel till convergence}
  \State Pick $\alpha$ solution proposals $\mathcal{P}\subset \mathcal{P_{\mbox{pool}}}$
  \State Pick $\beta$ solutions $\mathcal{S} \subset \mathcal{S_{\mbox{pool}}}$
  \State $S_i \leftarrow \mbox{Fuse}(S_i, \mathcal{P}, \mathcal{S})$
  \State Replaces the solution in $\mathcal{S}_{pool}$ with $S_i$
  \State [ Generates proposals and update $\mathcal{P}_{pool}$ ]
  \EndFor
  \EndProcedure
 \end{algorithmic}
\end{algorithm}

>>>>

Swarm Fusion has two main parameters $\alpha_i$ and $\beta_i$ (for each
thread $T_i$), determining the processing flow of the algorithm: In each
fusion step, the thread collects $\alpha_i$ solution proposals from the
proposal pool and $\beta_i$ solutions from the solution pool, following
a user-defined strategy or at random to be simple.
%
% One can further customize how to pick certain proposal generation
% schemes (as in ~\cite{delong}) or solutions.
Swarm Fusion framework is very flexible and yields various data
processing architectures as shown in Figure~\ref{fig:model}.
%
\begin{figure}[tb]
 \includegraphics[width=\columnwidth]{figure/model.pdf} \caption{Swarm
 Fusion architecture and its relationships to existing methods. The
 bottom right diagram shows the general Swarm fusion architecture, where
 each thread takes arbitrary number of solution proposals and concurrent
 solutions from other threads for fusion. The left two examples at the
 bottom row are Swarm fusion architecture with some restrictions, for
 which we provide comparative evaluations in
 Section~\ref{section:results}. Swarm fusion is a very flexible model,
 and it is easy to verify that existing methods such as
 alpha-expansion~\cite{alpha_expansion}, Fusion move~\cite{FM}, parallel
 alpha-expansion~\cite{delong}, or hierarchical
 fusion~\cite{delong_hierarchical_fusion,olga}, are all its special
 cases.}\label{fig:model}
\end{figure}
%
The bottom right configuration is the most general one, in which we
always fuse some solution proposals and some concurrent solutions
(i.e., $\alpha\ne 0, \beta \ne 0$).
%
Each fusion is multi-way (not binary) with a non-submodular energy, and
we use TRW~\cite{kolmogorov} for the fusion, while any other compatible
inference techniques can be used~\cite{opengm}. Of course, if one knows
that a certain fusion step is a binary fusion with submodular energy,
one can use graph-cuts instead~\cite{alpha_expansion_paper}. If a
certain fusion step is a binary fusion with non-submodular energy, one
can use QPBO~\cite{second_order_smoothness_stereo}.
%
Note that the threads are all synchronized in the figure for a
illustration purpose. In practice, all the threads run asynchronously
with a (read-write) lock on the data in the two pools (See Algorithm~\ref{algorithm:sf}).
%The asynchronous processing could be difficult for cloud parallel
%computing.
%
%
%
\begin{algorithm}
 \caption{Swarm Fusion method}
 \label{algorithm:sf}
 \begin{algorithmic}
  %\Procedure{Swarm Fusion method} {}
  \Procedure{} {$\alpha, \beta$}
  \State $\mathcal{S}_{pool} \leftarrow \emptyset$ //
  Solution pool
  \State Initialize $\mathcal{P}_{pool}$ // Proposal pool
  \ForEach{thread $T_i$}
  \State Initialize its solution $S_i$
  \EndFor
  \State
  \ForEach{thread $T_i$ in parallel till convergence}
  \State Pick $\alpha$ solution proposals $\mathcal{P}\subset \mathcal{P_{\mbox{pool}}}$
  \State Pick $\beta$ solutions $\mathcal{S} \subset \mathcal{S_{\mbox{pool}}}$
  \State $S_i \leftarrow \mbox{Fuse}(S_i, \mathcal{P}, \mathcal{S})$
  \State Replaces the solution in $\mathcal{S}_{pool}$ with $S_i$
  \State [ Generates proposals and update $\mathcal{P}_{pool}$ ]
  \EndFor
  \EndProcedure
 \end{algorithmic}
\end{algorithm}
